%
% This is an example of an acknowledgements page.  This is optional,
% and can contain anything you want to say.
%
%
%  Time-stamp: "[acknowl.tex] last modified by Scott Budge (scott) on 2011-08-08 (Monday, 8 August 2011) at 15:45:15 on goga"
%
%  Info: $Id$   USU
%  Revision: $Rev$
% $LastChangedDate$
% $LastChangedBy$
%

\begin{acknowledgments} 

This work would not have been realized without the help and support of the following people who graciously contributed to the work presented in this thesis.

Firstly, I would like to express my sincere gratitude to my advisor Prof. Gene Kogan for the continuous support of my thesis study and research, for his patience, encouragement, immense knowledge and expertise. I could not have imagined having a better mentor and advisor for my thesis study.

Besides my advisor, I would like to express my immense gratitude to my thesis professor Dr. Elizabeth P. Henaff. Her counsel and guidance helped me all through the research process and writing of this thesis. Without her continued guidance and stewardship, it would not have been possible to conduct this research.

I also would like to thank my pre-thesis instructor, Dana Karwas and Benedetta Piantella for helping shape the research and providing valuable insight when the project was in its nascent stage. 

I also would like to thank the rest of my thesis committee, mentors and advisors: Prof. Prof. Tega Brain, Prof. Daniel Shiffman, Prof. Jack Toolin, Prof. Mark Skwarek and Prof. Luke DuBois for their insightful remarks and encouragement, but also for the constructive feedbacks which inspired me to widen my research from various perspectives.

I thank my fellow peer in for the stimulating discussions and user testing for the prototype, and for all the collaboration and learning. Also, I would like to thank my friends in the following institution: New York University Tandon School of Engineering, Center For Data Science and Courant Institute of Mathematics. In particular, I am grateful to Prof. Iddo Drori for enlightening me the first glance of the research.

Finally, I would like to thank my friends and colleagues for supporting me generously throughout this thesis coursework.

\begin{flushright} 
Parvez A. Kose
\end{flushright}
\end{acknowledgments}

